Fusion Moves for Correlation Clustering

### 2014-11-12 paper/egpaper_for_review.tex
work on orposal gen

While we, contrary to~\cite{arbelaez_2006}, directly work on energies, we are interested in an 
agglomeration with respect to our energy function~\ref{eq:edgeproblem}.
For this we propose to use energy based agglomeration
with the following update rule:
Whenever there are multiple edges between 
a pair of nodes, these edges are merged into a single edge
by summing up their weights, since we 
minimize the sum of the cut edges.
We call HC with this update method Energy base Hierarchical Clustering (EHC).

@@

As discussed in \cite{Lempitsky-2010}, proposals
should have two properties: \emph{quality} 
and \emph{diversity}.
%
The quality of the individual proposals
ensures low energy solutions since the
result of the fusion cannot be higher then
the energy of the current best solution.
%
Diversity between the individual proposals
increase the chances to escape from local minima.
%
For correlation clustering fusion we add a third
property: \emph{size}.
The size of the contraction graph directly
depends on the number of connected components
in the proposal solution and the current best solution.
The extreme  case is a proposal where each 
node is in a separate connnected component.
Solving the fusion move with such a proposal
is equivalent to solving the original problem.
Solving the fusion move with a proposal with 
a single connected component will result 
in the current best solution.
Therefore the size of the proposals
should be small enough, such that solving
eq.~\ref{eq:edgeproblem} can
be done fast enough, but large enough to make
meaningful moves (??? this last sentence needs to be rewritten).

>>>>

While we, contrary to~\cite{arbelaez_2006}, directly work on energies, we are interesting in an 
agglomeration with respect to our energy function~\ref{eq:edgeproblem}.
For this we propose to use energy based agglomeration
with the following update rule:
Whenever there are multiple edges between 
a pair of nodes, these edges are merged into a single edge
by summing up their weights, since we 
minimize the sum of the cut edges.
We call HC with this update method Energy base Hierarchical Clustering (EHC).

@@

As discussed in~\cite{Lempitsky-2010}, proposals
should have two properties: \emph{quality} 
and \emph{diversity}.
%
A proposal have a high quality if it at least loacly
The quality of the individual proposals
ensures low energy solutions since the
result of the fusion cannot be higher then
the energy of the current best solution.
%
Diversity between the individual proposals
increase the chances to escape from local minima.
%
For correlation clustering fusion we add a third
property: \emph{size}.
The size of the contraction graph directly
depends on the number of connected components
in the proposal solution and the current best solution.
The extreme  case is a proposal where each 
node is in a separate connnected component.
Solving the fusion move with such a proposal
is equivalent to solving the original problem.
Solving the fusion move with a proposal with 
a single connected component will result 
in the current best solution.
Therefore the size of the proposals
should be small enough, such that solving
eq.~\ref{eq:edgeproblem} can
be done fast enough, but large enough to make
meaningful moves (??? this last sentence needs to be rewritten).
